---
title: "Reproducible Research - Notes"
author: "CC"
date: "November 28, 2016"
output: ioslides_presentation
---

## What is Reproducible Research About?

- Course Focus: How do you develop the score for Data Analysis? To communicate what you have done, and get others to know how they can reproduce the work. Writing dynamic code and sharing data. 

- Problem: No agreed upon platform/system for data analysis

## Concepts and Idea

- Reproducible Research: Make analytics data and code available so that others may reproduce findings
- *What do we need?*
- Analytics data are available
- Analytics code are available
- Documentation of code and data
- Standard means of distribution

## Script Everything

- Write it down, make the work reproducible

## Structure of Data Analysis

- Defining a question (narrow down question to simplify the problem)
- Determine what data you can access
    - Free data on web
    - Buy the data
    - Respect the terms of use
    - Generate it yourself
- Obtain the data

## Structure of Data Analysis (continued)

- Clean the data
- Exploratory data analysis
    - summaries
    - missing data
    - exploratory plots
    - exploratory analyses
- Statistical prediction/modeling
- Get a measure of uncertainty
- Interpret results
- Challenge results
Synthesize/write-up results

## Organize Your Analysis
- Data analysis files
    - Data
        - Raw data
        - Processed data
    - Figures
        - Exploratory figures
        - Final figures
    - R code
        - Raw / unused scripts
        - Final scripts
        - R Markdown files
    - Text
        - README files
        - Text of analysis / report

## Organize Your Analysis (continued)
- Raw data
- Processed data
- Exploratory figures
- Raw scripts
- Final scripts (clearly commented)
- R markdown files
- readme files (step-by-step instruction for analysis)
- Text of document








## Slide with R Code and Output

```{r}
summary(cars)
```

## Slide with Plot

```{r, echo=FALSE}
plot(cars)
```

