---
title: "Introduction to Markdown"
author: "CC"
date: "December 3, 2016"
output: ioslides_presentation
---

## Markdown
"Markdown is a text-to-HTML conversion tool for web writers. Markdown allows you to write using an easy-to-read, easy-to-write plain text format, then convert it to structurally valid XHTML (or HTML)"

## Markdown Syntax
- *Italics*
- **Bold**

1. first
1. qifeng
2. second
3. third

## Markdown Syntax
- Links
- [NBA](http://www.nba.com)

I spend so much time reading [R bloggers][1] and [Simply Statistics][2]!  
[1]: http://www.r-bloggers.com/ "R bloggers"  
[2]: http://simplystatistics.org/ "Simply Statistics"

## R Markdown
- Allows one to create documents containing "live" R code
- knitr package, markdown package, slidify package

## R Markdown Demo
```{r}
library(datasets)
data(airquality)
summary(airquality)
```

## Let's first make a pairs of the data

```{r}
pairs(airquality)
```

## Here is a regression model of ozone on wind, solar radiation, and temperature

```{r}
library(stats)
fit = lm(Ozone~Wind+Solar.R+Temp, data=airquality)
summary(fit)
```

## Slide with R Code and Output

```{r}
summary(cars)
```

## Slide with Plot

```{r, echo=FALSE}
plot(cars)
```

